### 2015-07-16 thesis/thesis/ack.tex
changes

I would like to thank my supervisors, Prof. Jamal Bentahar and Prof. Hadi Otrok for giving me the opportunity to work under their supervision. I am very grateful to them for their valuable suggestions and guidance throughout the preparation of this thesis. I learned a lot of valuable lessons which will be useful for me beyond the scope of this thesis, throughout my lifetime.

@@

Finally, I am very grateful to my parents for their understanding, encouragement and their endless support.

>>>>

I would like to thank my supervisors, Prof. Jamal Bentahar and Prof. Hadi Otrok for giving me the opportunity to work under their supervision. I am very grateful to them for their valuable suggestions and guidance throughout the preparation of this thesis. I learned a lot of valuable lessons which will be useful for me beyond the scope of this thesis throughout my lifetime. I also would like to thank Prof. Rabeb Mizouni for her significant help during my research work.

@@

Finally, I am very grateful to my fiance and colleague Atieh Saberi and my parents for their understanding, encouragement and their endless support.

### 2015-07-16 thesis/thesis/chap3/chap3.tex
changes

In this section, we discuss the experiments we performed for our
scenarios to validate the applicability and performance of our
proposed methods in realistic environments.
An XML SOAP based messaging system was implemented. We created a pool of web services and populated most of
their \emph{QoS} parameters from a real world web service dataset
\cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented
environment includes the QWS dataset by Eyhab Al-Masri and Qusay
H. Mahmoud freely available at:
http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}. To test
our methods, we formed around 10,000 random coalitions consisting
of 3 to 160 web services. In average, the communities were populated by 60 web
services. We implemented the
scenarios using Java and executed the experiments on an Intel Xeon
X3450 machine with 6GBs of memory.

@@

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3.5in]{Figures/s2_task_done.eps}
\includegraphics[width=3.5in]{Figures/s2_task_qos.eps}
\caption{Part (a): Cumulative number of tasks succesfully done. Part
(b): Average QoS of tasks performed.} \label{performancemany}
\end{figure}

@@

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=4in]{Figures/taxtation.eps}
\caption{Analysis of community subsiding coefficient $\lambda$ on
average community size (a), cost (b), number of tasks performed
(c), and average quality of service of tasks performed (d).}
\label{f_taxtation}
\end{figure*}

@@

\begin{figure*}%[!t]In the previous experiment, we considered the scenario where all
web services are stable, will not leave the group, and will
fulfill their promised QoS for a good period of time. However, in
real world scenarios of web services, this is not always the case.
This is the reason why the community coordinator would be interested in paying
web services in order to keep the group reliable from the end
user's point of view.
\centerline{\includegraphics[width=7in]{Figures/tax_dyn.eps}}
\caption{Analysis of community subsiding coefficient $\lambda$
having web service different stability levels of $\tau$ on average
community size, number of tasks performed, average quality of
service, and average cost/income of communities.}
\label{fig_dynamic_taxtation}
\end{figure*}

>>>>

In this section, we discuss the experiments we performed for our
scenarios to validate the applicability and performance of our
proposed methods in realistic environments.
An XML SOAP based messaging system was implemented. We created a pool of web services and populated most of
their \emph{QoS} parameters from a real world web service dataset
\cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented
environment includes the QWS dataset by Eyhab Al-Masri and Qusay
H. Mahmoud freely available at:
\url{http://www.uoguelph.ca/\textasciitilde qmahmoud/qws/}.}. To test
our methods, we formed around 10,000 random coalitions consisting
of 3 to 160 web services. In average, the communities were populated by 60 web
services. We implemented the
scenarios using Java and executed the experiments on an Intel Xeon
X3450 machine with 6GBs of memory.

@@

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=4in]{Figures/s2_task_done.eps}
\includegraphics[width=4in]{Figures/s2_task_qos.eps}
\caption{Part (a): Cumulative number of tasks succesfully done. Part
(b): Average QoS of tasks performed.} \label{performancemany}
\end{figure}

@@

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=5.5in]{Figures/taxtation.eps}
\caption{Analysis of community subsiding coefficient $\lambda$ on
average community size (a), cost (b), number of tasks performed
(c), and average quality of service of tasks performed (d).}
\label{f_taxtation}
\end{figure*}

@@

\begin{figure*}%[!t]In the previous experiment, we considered the scenario where all
web services are stable, will not leave the group, and will
fulfill their promised QoS for a good period of time. However, in
real world scenarios of web services, this is not always the case.
This is the reason why the community coordinator would be interested in paying
web services in order to keep the group reliable from the end
user's point of view.
\centerline{\includegraphics[width=7.5in]{Figures/tax_dyn.eps}}
\caption{Analysis of community subsiding coefficient $\lambda$
having web service different stability levels of $\tau$ on average
community size, number of tasks performed, average quality of
service, and average cost/income of communities.}
\label{fig_dynamic_taxtation}
\end{figure*}

### 2015-07-16 thesis/thesis/chap4/chap4.tex
changes

%We used a data set extracted from running web services. In this data set,
Each web service is associated with a number of quality metrics that reflect its non functional parameters. These web services operate in an online environment and are continuously assigned tasks to handle. %To engage in communities, we add the external features that reflect web services' utility as a result of joining other web services to form a community (see Section \ref{s:ef}). %The additional features are %computed based on two assumptions that we adopt for a community to be formed.
We used the web services data set provided in \cite{10.1109/ISSRE.2011.17}. The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}. %In this data set, each web service is associated with a number of features that reflect its functionality.
%Our raw data set provides us with 64 different time slots of extracted features for each web service.
Using this data, we built a synthetic data set that contains features of a large number of web services and communities in different time intervals. The goal is to use the data set to train a decision-making model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services. %To train our model, we build a decision tree as a benchmark for our decision making mechanism. The decision tree is made up by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services. The ultimate objective is to propose for each web service and community the best joint decision about forming a group that maximizes every one's utility.

@@

\section{Experiments}\label{s:experiments}
We implemented DDM in Java\footnote{Source code of implementation and data is available at: $https://github.com/Marooned202/DDM$}. We recall that we have extracted the set of features for 4532 web services in 64 different time slots through a data set provided in \cite{10.1109/ISSRE.2011.17}. By randomly choosing 86 web services out of this data set for each run, and selecting a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have been able to create 10,000 communities and evaluated the feature vectors and utilities they can have in the 64 time slots. This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities. Based on Equation \ref{u_c_load}, the utilities of these communities are estimated, and then the $gain$ matrix of size $|10,000 \times~ 10,000|$ of all possible ways of merging these 10,000 communities is generated\footnote {The template vector and $gain$ matrix generated are available at $https://github.com/Marooned202/DDM/tree/master/wsds/data/run$}. Based on the $gain$ matrix, each community has an ordered preference among other communities in the set.

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=5in]{figures/utility_gain.eps}
\caption{DDM against Rational: utility gain }
\label{utility_gain_mlisa_and_rational}
\end{figure}

\begin{figure}%[!t]
\centering
\includegraphics[width=5in]{figures/utility_ratio.eps}
\caption{DDM against Rational: ratio of utility gain}
\label{utility_gain_mlisa_and_rational_ratio}
\end{figure}

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=4in]{figures/roc.eps}
\caption{RoC Curve}
\label{roc5}
\end{figure}

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=4in]{figures/stats1.eps}
\caption{Overall utility of all the communities}
\label{stats1}
\end{figure}

\begin{figure}%[!t]
\centering
\includegraphics[width=4in]{figures/stats2.eps}
\caption{Utility gain over time}
\label{stats2}
\end{figure}

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=4in]{figures/stats3.eps}
\caption{Average community size}
\label{stats3}
\end{figure}

>>>>

%We used a data set extracted from running web services. In this data set,
Each web service is associated with a number of quality metrics that reflect its non functional parameters. These web services operate in an online environment and are continuously assigned tasks to handle. %To engage in communities, we add the external features that reflect web services' utility as a result of joining other web services to form a community (see Section \ref{s:ef}). %The additional features are %computed based on two assumptions that we adopt for a community to be formed.
We used the web services data set provided in \cite{10.1109/ISSRE.2011.17}. The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{\url{http://www.wsdream.net/}}. %In this data set, each web service is associated with a number of features that reflect its functionality.
%Our raw data set provides us with 64 different time slots of extracted features for each web service.
Using this data, we built a synthetic data set that contains features of a large number of web services and communities in different time intervals. The goal is to use the data set to train a decision-making model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services. %To train our model, we build a decision tree as a benchmark for our decision making mechanism. The decision tree is made up by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services. The ultimate objective is to propose for each web service and community the best joint decision about forming a group that maximizes every one's utility.

@@

\section{Experiments}\label{s:experiments}
We implemented DDM in Java\footnote{Source code of implementation and data is available at: \url{https://github.com/Marooned202/DDM}}. We recall that we have extracted the set of features for 4532 web services in 64 different time slots through a data set provided in \cite{10.1109/ISSRE.2011.17}. By randomly choosing 86 web services out of this data set for each run, and selecting a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have been able to create 10,000 communities and evaluated the feature vectors and utilities they can have in the 64 time slots. This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities. Based on Equation \ref{u_c_load}, the utilities of these communities are estimated, and then the $gain$ matrix of size $|10,000 \times~ 10,000|$ of all possible ways of merging these 10,000 communities is generated\footnote {The template vector and $gain$ matrix generated are available at \url{https://github.com/Marooned202/DDM/tree/master/wsds/data/run}}. Based on the $gain$ matrix, each community has an ordered preference among other communities in the set.

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=5.5in]{figures/utility_gain.eps}
\caption{DDM against Rational: utility gain }
\label{utility_gain_mlisa_and_rational}
\end{figure}

\begin{figure}%[!t]
\centering
\includegraphics[width=5.5in]{figures/utility_ratio.eps}
\caption{DDM against Rational: ratio of utility gain}
\label{utility_gain_mlisa_and_rational_ratio}
\end{figure}

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=5in]{figures/roc.eps}
\caption{RoC Curve}
\label{roc5}
\end{figure}

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=5.5in]{figures/stats1.eps}
\caption{Overall utility of all the communities}
\label{stats1}
\end{figure}

\begin{figure}%[!t]
\centering
\includegraphics[width=5.5in]{figures/stats2.eps}
\caption{Utility gain over time}
\label{stats2}
\end{figure}

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=5.5in]{figures/stats3.eps}
\caption{Average community size}
\label{stats3}
\end{figure}
